NumPy---Array Programming in Python

### 2020-01-22 body.tex
Add some notes

NumPy was initially developed by students, faculty, and researchers in their
spare time to provide a modern array programming library for Python.  They were
influenced by their experiences with powerful interactive programming languages
for scientific computing like Yorick \cite{munro1995using} as well as
commercial languages and environments like IDL and Matlab.  They also
frequently developed code from scratch to solve their own or their colleagues'
problems, often in low-level languages that preceded Python like as Fortran
\cite{dongarra2008netlib} and C.  It is also hard to imagine that scientific
Python was not in part influenced by its contemporaries, such as ROOT.

% Fortran / C

@@

% S:
%
% Thinking about enabling factors, I'd characterize them into three categories:
%
% - Practical
% - Philosophical
% - Social
%
% E.g., practical: reason why we use Python (learn one language for
% everything); students don't have money, so want to avoid impracticalities of
% license dongles/servers, etc.
%
% Philosophical: science should be open, transparent; our software should be
% controlled by scientists, not designers that we don't have access to
%
% Social: joy of building these things together, friendly welcome into the
% community for many of us---appreciation of our work and hours

>>>>

NumPy was initially developed by students, faculty, and researchers in their
spare time to provide a modern array programming library for Python.  They were
influenced by their experiences with powerful interactive programming languages
for scientific computing like Yorick \cite{munro1995using} as well as
commercial languages and environments like IDL and Matlab.  They also
frequently developed code from scratch to solve their own or their colleagues'
problems, often in low-level languages that preceded Python like Fortran
\cite{dongarra2008netlib} and C.

% Fortran / C
% A few sentences on the history of array programming, referencing APL and Fortran, are missing.

@@

% S:
%
% Thinking about enabling factors, I'd characterize them into three categories:
%
% - Practical
% - Philosophical
% - Social
% - Technical
%
% E.g., practical: reason why we use Python (learn one language for
% everything); students don't have money, so want to avoid impracticalities of
% license dongles/servers, etc.
%
% Philosophical: science should be open, transparent; our software should be
% controlled by scientists, not designers that we don't have access to
%
% Social: joy of building these things together, friendly welcome into the
% community for many of us---appreciation of our work and hours
